Notes on the low density parameters in {\tt MAESTRO}

### 2009-02-17 docs/lo_density/lo_density.tex
updated info about cutoff coordinates

@@

\item After we initilize the base state in {\tt varden} and at the
  beginning of {\tt advance\_timestep}, We compute the coordinate
  associated with {\tt anelastic\_cutoff}, {\tt anelastic\_cutoff\_coord}.  
  This is done by setting ${\tt anelastic\_cutoff\_coord}= r$ as soon as 
  $\rho_0(r) <$ {\tt anelastic\_cutoff}.

@@

\item After we initilize the base state in {\tt varden} and at the
  beginning of {\tt advance\_timestep}, We compute the coordinate
  associated with {\tt base\_cutoff\_density}, {\tt
    base\_cutoff\_density\_coord}.  This is done by setting ${\tt
    base\_cutoff\_density\_coord}= r$ as soon as $\rho_0(r) <$ {\tt
    base\_cutoff\_density}.

@@

\item In {\tt enforce\_HSE}, we set $p_0(r) = p_0(r-1)$ for 
  $r\in[{\tt base\_cutoff\_density\_coord}-1]$

@@

\begin{itemize}
\item After we initilize the base state in {\tt varden} and at the
  beginning of {\tt advance\_timestep}, We compute the coordinate
  associated with {\tt burning\_cutoff\_density}, {\tt
    burning\_cutoff\_density\_coord}.  This is done by setting ${\tt
    burning\_cutoff\_density\_coord}= r$ as soon as $\rho_0(r) <$ {\tt
    burning\_cutoff\_density}.

\item In {\tt react\_state}, we only call the burner if $\rho >$ {\tt
  burning\_cutoff\_density}.
%\item In {\tt react\_state}, we only call the burner for $r\in[{\tt r\_start\_coord},{\tt burning\_cutoff\_density\_coord}-1]$.
\end{itemize}

>>>>

\section{Computing the Cutoff Values}

At several points in the algorithm, we compute {\tt anelastic\_cutoff\_coord}, 
{\tt base\_cutoff\_density\_coord}, and {\tt burning\_cutoff\_density\_coord} by 
setting the corresponding coordinate equal to $r$ as soon as $\rho_0(r)$ is less than 
that particular cutoff value.  We set the coordinates at the following points in the
code:

\item After we initialize the base state in {\tt varden}.

\item At the beginning of {\tt advance\_timestep}.

\item After each call to {\tt advect\_base\_dens}.

\item After each call to {\tt correct\_base} in spherical 
  (or call to {\tt average} in plane-parallel.

@@

@@

@@

\item In {\tt enforce\_HSE}, we set $p_0(r) = p_0(r-1)$ for 
  $r\in[{\tt base\_cutoff\_density\_coord}-1,{\tt r\_end\_coord}]$

@@

\item In {\tt react\_state}, we only call the burner if 
  $\rho >$ {\tt burning\_cutoff\_density}.
